Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-14 paper.tex
refactored 4 completely

\subsubsection{Dynamic Language Features}
Conceptually, we identified two language features for which symbolic execution
failed frequently. As stated in Section \ref{sec:workflow}, dynamic web
applications are staged and client page output is computed at runtime. Symbolic
execution has shown to be a useful technique to approximate dynamically
generated output in theory, though it is challenged by language features that
require concrete information rather than symbolic information at runtime. In particular, this
applies to language features that provide access to reusable code of the web
application: include expressions and function calls.

@@

We started classifying missed output candidates by their string literal
context. As the classification statistics in Figure \ref{coverage} illustrate,
for almost all systems (except for \textsf{AddressBook} and \textsf{TimeClock})
not-reached output candidates had a function context.

\subsubsection{Inaccessible Dynamic Features}
\label{sec:inaccessible}
For both cases of context, either inclusion of a script file failed, or a
function call failed. If an HTML file is not part of the output, it also is
never reached, i.e., included. An include can fail due to various reasons, such
as an imprecise evaluation of the include expression returning a symbolic
value, or simply a missing file.

For a function to be never reached there are several scenarios: A function is
undefined at runtime if the corresponding script file is never included. In
turn, if the function is defined at runtime the function can either be dead
code if there is no call site for this function, or the function call failed.
In PHP there are several ways to call a function beside direct call sites. The
language offers indirect call mechanisms like callback-commands or an
evaluation function that parses and evaluates PHP source code as strings.

Given a symbolic value, indirect call mechanisms like callback-commands are
likely to fail since target function name and the symbolic value do not match.
This also applies for the evaluation of include expressions as concrete values
representing include targets can be included, but any include target containing
symbolic values is ambiguous.

\subsubsection{Why did includes fail?}
\label{WhyDidIncludesFail}
To better understand include expression evaluation, we use another metric to
approach accuracy from a different angle: We measure (1) the ratio of reached
include expressions and the total number of include expressions in a system
respectively (coverage of include expressions), and (2) the ratio of
successfully resolved include expressions and reached include expressions in a
system (resolution success rate). For a most accurate result all include
expressions are reached and resolved.

For include expressions we sampled failed attempts and manually evaluated the
cause of failure. We identified for (1) that all failed attempts were dynamic
include expressions, i.e., those which were resolved at runtime and were
assembled from fragments of environment-dependent information including
database retrievals, user input, or files. Consequently, the resolved include
expressions contained symbolic values which did not represent identifiable
script files.

Finally, we measured for include expressions the overall reach coverage and the
overall resolution success rate per system. As illustrated in Figure
\ref{fig:include_coverage_results}, except for the small-scale systems and two
recent small-scale systems we did not even really reach a great portion of
include expressions, although for most systems the resolution success rate was
over 80 percent. Nevertheless, one failed attempt to include a script file can
result in a cascade of missing more include expressions as the include target
script is not executed.

The callgraph snippets in Figure \ref{fig:callgraph} illustrate the idea of
detecting the functions’ access points: The nodes at the top depict callback
candidates, the nodes at the bottom with labels X, Y, and Z depict function
definitions containing not-reached output candidates. In Figure
\ref{fig:callgraph} function X can only be accessed through callback
candidates, as for Figure \ref{fig:callgraph} function Y can be partially
accessed by callback candidates, whereas function Z is never accessible through
callback candidates.

% Callback candidate description
\begin{figure}[t!]
	%\centering
	\includegraphics[scale=0.55]{images-paper/callgraph_cases}
    \caption{Callgraph analysis: The bottom nodes represent functions containing missed output candidates, the top nodes depict entry points to them.}
    \label{fig:callgraph} output candidates we measured how many of those functions were only, or partially accessibly through indirect calling mechanisms (see Section \ref{sec:inaccessible}). As Figure \ref{fig:output_candidate_explanation} illustrates, around 80 percent (except for \textsf{TimeClock}) all missed output candidates of each system were only accessible through callback candidates, i.e., functions that are only accessible through indirect calling mechanisms.

\end{figure}

Like for include expressions, we again sampled dead function cases and
identified the lack of direct call sites to those functions. As described in
Section \ref{sec:inaccessible}, functions despite having no direct call sites
were called through indirect call features. We identified dynamically assembled
expressions (function names) to be responsible for failed attempts of calling a
function indirectly as the resolved function name eventually contained symbolic
values. These expressions, as well as include expressions, contained
information dependent on the system environment.

For failed function calls to functions containing not-reached

@@

\section{Lessons Learned}
\textcolor{blue}{\Blindtext}

\section{Related Work} \label{sec:related_work}
\cite{Hills:2013:ESP:2483760.2483786}
\cite{wassermann2007sound,minamide2005static}
\textcolor{blue}{\blindtext\blindtext}

@@

\newpage
%References
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

>>>>

\subsubsection{Dynamic Language Features}
\label{sec:experiment_dynamicfeaturess} 
Conceptually, we identified two language features for which symbolic execution
failed frequently. As stated in Section \ref{sec:workflow}, dynamic web
applications are staged and client page output is computed at runtime. Symbolic
execution has shown to be a useful technique to approximate dynamically
generated output in theory, though it is challenged by language features that
require concrete information rather than symbolic information at runtime. In particular, this
applies to language features that provide access to reusable code of the web
application: include expressions and function calls.

@@

@@

We started classifying missed output candidates by their string literal
context. As the classification statistics in Figure \ref{coverage} illustrate,
for almost all systems tested (except for \textsf{AddressBook} and
\textsf{TimeClock}) not-reached output candidates had a function context.

%\subsubsection{Inaccessible Dynamic Features} \label{sec:inaccessible}
For both cases of context, either inclusion of a script file failed, or a
function call failed. If an HTML file is not part of the output, it also is
never reached, i.e., included. An include can fail due to various reasons, such
as an imprecise evaluation of the include expression returning a symbolic
value, or simply a missing file.

For a function to be never reached there are several scenarios: A function is
undefined at runtime if the corresponding script file is never included. In
turn, if the function is defined at runtime, the function is dead
code if there is no call site for this function, or the function is only called
indirectly and the function name could not be resolved accurately. In PHP there
are several ways to call a function beside direct call sites. 
%The language offers indirect call mechanisms like callback-commands or an
% evaluation function that parses and evaluates PHP source code as strings.

Given a symbolic value, indirect call mechanisms like callback-commands are
likely to fail since target function name and the symbolic value do not match.
This also applies for the evaluation of include expressions as concrete values
representing include targets can be included, but any include target containing
symbolic values is ambiguous. Since it is unlikely that all functions containing
missed output candidates are dead code having no call site (direct or
indirect) at all, in Section \ref{WhyDidFunctionCallsFail} we further
investigate how many functions fail due to inaccurately resolved indirect
function calls. Moreover, we evaluate the accuracy of evaluation of include
expressions in the next section.

\subsubsection{Why did includes fail?}
\label{WhyDidIncludesFail}
From Section \ref{sec:experiment_dynamicfeaturess} we learn that include
expressions can not be evaluated accurately for symbolic values, and from the
previous Section \ref{WhatLiteralsDidWeMiss?} that very little of missed output
candidates can be explained by simply missing to include a file. To better
understand the impact of include expression resolution throughout analyzing
systems, we construct two additional metrics. First, we are interested in how
many include expressions throughout the execution we actually reach in a system.
Therefore we introduce the metric \emph{reach coverage for include expressions}
as the ratio of reached include expressions and the total number of reach
expressions in a system to check whether failed includes may have caused
subsequent include expressions and so on. Second, we measure how successful
include expressions are resolved.

Figure \ref{fig:include_coverage_results} illustrates the classification of
include expressions for each system: We can either reach an include expression
and successfully resolve it, or not. Or, we did not reach an include expression at all. 
Figure \ref{fig:include_coverage_results} indicates that except for the
small-scale systems as well as \sf{Anchor} and \sf{Nibbleblog} we did not really
reach a great portion of include expressions, although for most systems the
resolution success rate was over 80 percent. Note that one failed attempt
to include a script file can result in a cascade of missing more include
expressions as the include target script file is not included and executed.

The callgraph snippets in Figure \ref{fig:callgraph} illustrate the idea of
detecting the functions’ access points: The nodes at the top depict callback
candidates, the nodes at the bottom with labels \tt{X}, \tt{Y}, and \tt{Z}
depict function definitions containing not-reached output candidates. In Figure
\ref{fig:callgraph} function \tt{X} can only be accessed through callback
candidates, as for Figure \ref{fig:callgraph} function \tt{Y} can be partially
accessed by callback candidates, whereas function \tt{Z} is never accessible
through callback candidates.

% Callback candidate description
\begin{figure}[t!]
	%\centering
	\includegraphics[scale=0.55]{images-paper/callgraph_cases}
    \caption{Callgraph analysis: The bottom nodes represent functions
    containing missed output candidates, the top nodes depict entry points to
    them.}
    \label{fig:callgraph} 
\end{figure}

%Like for include expressions, we again sampled dead function cases and
% identified the lack of direct call sites to those functions. As described in
% Section \ref{sec:inaccessible}, functions despite having no direct call sites
% were called through indirect call features. We identified dynamically
% assembled expressions (function names) to be responsible for failed attempts
% of calling a function indirectly as the resolved function name eventually
% contained symbolic values. These expressions, as well as include expressions,
% contained information dependent on the system environment.

For failed function calls to functions containing not-reached output
candidates we measured how many of those functions were only, or
partially accessibly through indirect calling mechanisms (see Section
\ref{sec:experiment_dynamicfeaturess}). As Figure
\ref{fig:output_candidate_explanation} illustrates, around 80 percent (except
for \sf{TimeClock}) all missed output candidates of each system were only
accessible through callback candidates, i.e., functions that are only
accessible through indirect calling mechanisms.

\section{Lessons Learned}
%\textcolor{blue}{\Blindtext}

\section{Related Work} \label{sec:related_work}
\cite{Hills:2013:ESP:2483760.2483786}
\cite{wassermann2007sound,minamide2005static}
%\textcolor{blue}{\blindtext\blindtext}

@@

%\newpage
%References
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}
